---
title: "check_for_distributions"
author: "Martyna"
date: "2024-03-31"
output: pdf_document
---

```{r}
library(brms)
```

```{r}
data<- read.csv('data/df_ddm.csv')
```

1. Gaussian Distribution Model
This first model assumes that the reaction times follow a Gaussian (normal) distribution. It's a straightforward model where sacc_time is predicted by the intercept alone 

```{r}
# Model with Gaussian distribution
gaussian_model <- brm(
  formula = sacc_time ~ 1, 
  data = data, 
  family = gaussian()
)
```
2. Mixture of Two Gaussians Model
For the second model, we assume a bimodal distribution by modeling the data as a mixture of two Gaussians. This model is more complex and can capture data that m

```{r}
# Model with a mixture of two Gaussians
bimodal_model <- brm(
  formula = sacc_time ~ 1, 
  data = data, 
  family = mixture(gaussian, gaussian),
  chains = 2, iter = 4000 # Adjust these parameters as needed
)

summary(bimodal_model)

```

3. Model with a Proportion Parameter (Theta)
The third model involves specifying a distribution that allows for adjusting the proportion of the distribution across different components, such as the arms of a beta distribution or the components in a mixture model. 

Here, I'm using a mixture model as an example to include a proportion parameter (theta), which controls the mixture between the two Gaussian components

```{r}
# Model with a proportion parameter theta in a mixture of two Gaussians
theta_model <- brm(
  formula = sacc_time ~ 1, 
  data = data, 
  family = mixture(gaussian, gaussian),
  prior = c(set_prior("normal(0,5)", class = "b"),
            set_prior("lkj(2)", class = "cor"),
            set_prior("dirichlet(1,1)", class = "theta")), # Prior for theta
  chains = 2, iter = 4000 
)

summary(theta_model)
```
